Miniproject - Algebraic Geometry

### 2021-12-06 Algebraic geometry/submission.tex
Proved first part of important lemma

    However by Lemma~\ref{prop:linear_transform_extpow} we now get
    \begin{align*}
        0 =& 0 \wedge \Bigl( \sum_j a_{2j} v_j \Bigr) \wedge ... \wedge \Bigl( \sum_j a_{dj} v_j \Bigr) = \Bigl( \sum_j a_{1j} v_j \Bigr) \wedge ... \wedge \Bigl( \sum_j a_{dj} v_j \Bigr) \\
        =& \det(A) (v_1 \wedge ... \wedge v_d)
    \end{align*}
    and so $v = v_1 \wedge ... \wedge v_d = 0$ as $\det(A) \neq 0$.
    However, $v$ was a representative of a point in $\Proj(\extpow^d V)$, a contradiction.
    The claim follows.
\end{proof}
\end{document}

>>>>

    However by Lemma~\ref{prop:linear_transform_extpow} we now get
    \begin{align*}
        0 =& 0 \wedge \Bigl( \sum_j a_{2j} v_j \Bigr) \wedge ... \wedge \Bigl( \sum_j a_{dj} v_j \Bigr) = \Bigl( \sum_j a_{1j} v_j \Bigr) \wedge ... \wedge \Bigl( \sum_j a_{dj} v_j \Bigr) \\
        =& \det(A) (v_1 \wedge ... \wedge v_d)
    \end{align*}
    and so $v = v_1 \wedge ... \wedge v_d = 0$ as $\det(A) \neq 0$.
    However, $v$ was a representative of a point in $\Proj(\extpow^d V)$, a contradiction.
    The claim follows.
\end{proof}
\begin{definition}
    Let $\Gr(d, n) := \Gr(d, k^n)$.
\end{definition}
In the lecture, we considered an embedding of $\Gr(d, n)$ into projective space given by minors of the basis matrix.
This corresponds to the following definition.
\begin{definition}
    Define the map
    \begin{align*}
        \rho: \Gr(d, n) &\to \Proj\Bigl(k^{\{1, ..., n\}^{(d)}}\Bigr) \cong \Proj^{{n \choose d} - 1}, \\
        \vspan\{v_1, ..., v_d\} &\mapsto \Bigl[ \det\left(\begin{matrix}
            v_{1i_1} & ... & v_{di_1} \\
            \vdots & \ddots & \vdots \\
            v_{1i_d} & ... & v_{di_d}
        \end{matrix}\right) \Bigr]_{\{i_1, ..., i_d\} \in \{1, ..., n\}^{(d)}}
    \end{align*}
    where $\{1, ..., n\}^{(d)} := \{ I \subset \{1, ..., n\} \ | \ \#I = d \}$ is the set of all $d$-element subsets of $\{1, ..., n\}$.
\end{definition}
\begin{lemma}
    There is a linear isomorphism
    \begin{align*}
        f: \extpow^d k^n &\to k^{\{1, ..., n\}^{(d)}}, \\
        \sum_j v_1^{(j)} \wedge ... \wedge v_d^{(j)} &\mapsto \Bigl( \sum_j \det\left(\begin{matrix}
            v_{1i_1}^{(j)} & ... & v_{di_1}^{(j)} \\
            \vdots & \ddots & \vdots \\
            v_{1i_d}^{(j)} & ... & v_{di_d}^{(j)}
        \end{matrix}\right) \Bigr)_{\{i_1, ..., i_d\} \in \{1, ..., n\}^{(d)}}
    \end{align*}
\end{lemma}
\begin{proof}
    For vectors $v_1, ..., v_d$ and $I = \{i_1, ..., i_d\} \in \{1, ..., n\}^{(d)}$ write
    \begin{equation*}
        A_I(v_1, ..., v_d) := \left(\begin{matrix*}
            v_{1i_1} & ... & v_{di_1} \\
            \vdots & \ddots & \vdots \\
            v_{1i_d} & ... & v_{di_d}
        \end{matrix*}\right)
    \end{equation*}
    First of all, we show that $f$ is well-defined.
    Note that the tensor product can be described as
    \begin{align*}
        V^{\otimes d} := k^{V \times ...\times V} / \vspan\{ &\bigl(v_1 \otimes ... \otimes v_{i - 1} \otimes \bigl(v_i + v'_i\bigl) \otimes v_{i + 1} \otimes ... \otimes v_d\bigl) \\
        &- \bigl(v_1 \otimes ... \otimes v_d\bigl) - \bigl(v_1 \otimes ... \otimes v_{i - 1} \otimes v'_i \otimes v_{i + 1} \otimes ... \otimes v_d\bigl), \\
        & \bigl(v_1 \otimes ... \otimes v_{i - 1} \otimes \lambda v_i \otimes v_{i + 1} \otimes ... \otimes v_d\bigl) \\
        &- \lambda\bigl(v_1 \otimes ... \otimes v_{i - 1} \otimes v_i \otimes v_{i + 1} \otimes ... \otimes v_d\bigl) \ | \ i \leq d, v_j, v'_i \in V\}
    \end{align*}
    where $v_1 \otimes ... \otimes v_d := \mathbb{1}_{(v_1, ..., v_d)}$.
    Hence the external power can be described as
    \begin{align*}
        \extpow^d V := k^{V \times ... \times V} / \vspan\Bigl\{ &\bigl(v_1 \otimes ... \otimes v_{i - 1} \otimes \bigl(v_i + v'_i\bigl) \otimes v_{i + 1} \otimes ... \otimes v_d\bigl) \\
        &- \bigl(v_1 \otimes ... \otimes v_d\bigl) - \bigl(v_1 \otimes ... \otimes v_{i - 1} \otimes v'_i \otimes v_{i + 1} \otimes ... \otimes v_d\bigl), \\
        & \bigl(v_1 \otimes ... \otimes v_{i - 1} \otimes \lambda v_i \otimes v_{i + 1} \otimes ... \otimes v_d\bigl) \\
        &- \lambda\bigl(v_1 \otimes ... \otimes v_{i - 1} \otimes v_i \otimes v_{i + 1} \otimes ... \otimes v_d\bigl), \\
        &v_1 \otimes ... v_{j - 1} \otimes (v_j \otimes v_{j + 1} + v_{j + 1} \otimes v_j) \otimes v_{j + 1} \otimes ... \otimes v_d \\
        &\quad | \ i \leq d, \ j \leq d - 1, \ v_1, ..., v_d, v'_i \in V\Bigr\}
    \end{align*}
    So it suffices to show that for all $I \in \{1, ..., n\}^{(d)}$ and vectors $v_1, ..., v_d, v'_i \in V$
    \begin{align*}
        \det(A_I(v_1, ..., v_i + v'_i, ..., v_d)) = \det(A_I(v_1, ..., v_d)) + \det(A_I(v_1, ..., v'_i, ..., v_d))
    \end{align*}
    and
    \begin{align*}
        \det(A_I(v_1, ..., \lambda v_i, ..., v_d)) = \lambda\det(A_I(v_1, ..., v_d))
    \end{align*}
    and
    \begin{equation*}
        \det(A_I(v_1, ..., v_{j + 1}, v_j, ..., v_d)) = -\det(A_I(v_1, ..., v_d))
    \end{equation*}
    However, these properties follow from the well-known properties of the determinant.
    In particular, $\det$ is linear in each column and swapping columns negates the determinant.
    It follows that $f$ is indeed well-defined.

    It is clear by definition that $f$ is linear, so it is left to show that it is bijective. 
\end{proof}
\end{document}
